Preliminary Thesis Defence

### 2013-11-14 draft.Rnw
add CDC citation

Another deviation is the usage of \textcite{who2006child} in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.

>>>>

Another deviation is the usage of \textcite{who2006child} in stead of \textcite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence.
